Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-16 longoutput.tex
Fix bugs

\begin{theorem}
	Let $$H\in\spn\mathcal{G}_{XZ}$$ with ground state $\psi$ with the following properties:
	\begin{itemize}
		\item $\braket{\psi|H|\psi}=0$
		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	\end{itemize}
	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$. Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$. This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
\end{theorem}

@@

We scale the Hamiltonian.
$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
$$p_S=\frac{|d_S|}{D}=O(T^4)$$
$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$

Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
Which is simple to estimate by doing the measurements corresponding to $S$. The measurement result is $\pm1$, so it can be modeled as a bernoulli distribution with known expected value. The rest is simple number crunching. Note that $|d_S|=O(\poly(T))$.

\subsection{Analysis and amplification}

>>>>

\begin{theorem}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$
	with ground state $\psi$ with the following properties:
	\begin{itemize}
		\item $\braket{\psi|H|\psi}=0$
		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	\end{itemize}
	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$. Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$. This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
\end{theorem}

@@

We scale the Hamiltonian.
$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
$$p_S=\frac{|d_S|}{D}=O(\poly(T))$$
$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$

Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
Which is simple to estimate by picking and doing the measurements corresponding to $S$. The measurement result is $\pm1$. It can be modeled as a Bernoulli distribution with known expected value. The rest is simple number crunching.
\subsection{Analysis and amplification}
